### 2018-03-27 latex/sc18/prelims.tex
Some minor prelims work

\begin{itemize}
	\item tensor notation, Hadamard, Khatri-Rao, MTTKRP
	\item NNCP definition
	\item BCD/ALS
	\begin{itemize}
		\item MU, HALS, BPP, Nesterov, ADMM
	\end{itemize}
	\item MPI collectives
\end{itemize}

>>>>

	Tensors will be denoted using Euler script (e.g., $\T{T}$), matrices will be denoted (e.g., $\M{M}$), vectors will be denoted as lower case bold face type (e.g., $\V{v}$), and scalars will not be bolded (e.g., $s$). Matlab style notation will be sued to index into tensors, matrices, and vectors. For example, $\M{M}(:,c)$ gives the cth column of the matrix M.
	The Hadamard product is the element wise matrix product and will be denoted using $*$. 
	The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. It can be thought of as a series row-wise Hadamard products s.t. \\$\M{K}(0:) = \M{A}(0,:) * \M{B}(0,:)\\ \M{K}(1:) = \M{A}(0,:) * \M{B}(1,:)  \\.\\.\\. \\ \M{K}(I_{A}I_{B} - 1,:) = \M{A}(I_{A}-1,:) * \M{B}(I_{B}-1,:)$

\begin{itemize}
	%\item tensor notation, Hadamard, Khatri-Rao, 
	\item NNCP definition
	\item BCD/ALS
	\begin{itemize}
		\item MU, HALS, BPP, Nesterov, ADMM
	\end{itemize}
	\item MPI collectives
\end{itemize}
